---
title: "Project"
author: "pash"
date: "9/30/2020"
output: html_document
---

PROJECT
Patience
02/10/2020
                             INTRODUCTION

TOPIC:Linear Regression Analysis to determine the dependency of  Total Compensation on Salaries.
This will help identify the significate relationship  between the dependent and independent variables.

                           PROBLEM STATEMENT
                           
Developing analysis to predict and explain Total compensation on Salaries.

                            
DATA SOURCE:data.world 
salary and benefits paid to City employees for (a year as reckoned for taxing or accounting purposes)fiscal year.
where y= Total Compensation, x=Salaries.

```{r}
dt<-read.csv("Employee_Compensation_Sf.csv",header =T)
dt
```

```{r}
dt<-na.omit(dt)
dt
```

```{r}
library(ggplot2)
ggplot(dt,aes(x=Salaries,y=Total.Compensation)) + geom_point()+ geom_smooth(method = "lm")+labs(title = "Relationship between Salaries and Total.Compensation")
```
# The relationship between the Total.Compensation  and Salaries is a very strong positive relationship.

```{r}
mod1<-lm(Total.Compensation~Salaries, data= dt)
summary(mod1)
```
# the output indicates that the linear regression equation is
 y = 4.601e+03 + 1.476e+00(Salaries)
 
# the p-value 2.2e-16 indicates that Salaries have significance over Total.compensation
# for the slope, for every increase in unit Salaries, the Total.Compensation increases by 1.476e+00.
# Adjusted R_squared value which is 0.946, means that 94.6% of the total variation in Total.Compensation can be explained by the independent variable Salaries.

```{r}
head(mod1$residuals)
```
```{r}
dt$residuals<-mod1$residuals
head(dt$residuals)
```

```{r}
library(ggplot2)
ggplot(dt,aes(x=residuals)) + geom_histogram()

```
```{r}
par(mfrow=c(2,2))
plot(mod1)
ggplot(dt,aes(x=residuals)) + geom_histogram()
```
# The assumption of the normality of residuals has been voilated.
# the constant variable assumption is not met  cause there is pattern of points in the Residuals and Fitted plot.

CONCLUSION:



                            









          
